---
title: "p8105_hw5_xs2447"
output: github_document
---
Basic setting
```{r}
library(tidyverse)
library(leaflet)
library(gghighlight)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

##Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state !=  "TulsaAl")
```

Let's focus on Baltimore, MD

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>% pull(n))

baltimore_test %>% 
  broom::tidy()
```

Let's try to iterate across cities!

First off, write a function and test it on a few sample cities

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

  city_test = 
    prop.test(
    x = city_summary %>% pull(unsolved), 
    n = city_summary %>% pull(n))

  return(city_test)
  
}

prop_test_function(baltimore_df)


homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```

Try to make a plot showing estimates and confidence intervals.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


## Problem 2

Create name list

```{r}
name_df = tibble(
  name = list.files("./data/zip_data", full.names = TRUE))
```

Read csv and tidy up

```{r}
study_df = name_df %>% 
  mutate(data = map(name, ~read_csv(.x))) %>% 
  unnest(data) %>% 
  mutate(name = str_remove(name, "./data/zip_data/"),
         name = str_remove(name, ".csv")) %>% 
  separate(name, c("arm","ID"), sep = "_", remove = FALSE) %>% 
  mutate(arm = recode(arm, con = "control", exp = "experiment"))

```

Make a spaghetti plot

```{r}
study_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value",
    names_prefix = "week_"
  ) %>% 
  ggplot(aes(x = week, y = value, group = name, color = arm)) + 
  geom_line()
  
```

From the spaghetti plot, we can see that the observations values in experiment are generally increasing while control group's values have no uptrend in long term. All the observation values in experiment are higher than the values in the control groups starts from week 7.  

## Problem 3

```{r}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function.

```{r}
fill_in_missing = function(vector) {
  if (is.numeric(vector)) {
    
    fill = replace_na(vector, mean(vector, na.rm = TRUE))
    
  }
  
  if (is.character(vector)) {
    
    fill = replace_na(vector, "virginica")
    
  }
  
  return(fill)
}
```

Apply the function

```{r}
iris_with_fill = 
  iris_with_missing %>% 
  map_dfr(~fill_in_missing(.x))

iris_with_fill
```

